The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-09 article.tex
Include optimised path fingerprint times and table caption.

>>>>

\subsection*{Table ? - Summary of systematic benchmark comparing v1.4.19 to \cdkversion{}.}\label{tab:benchmark}
  The total elapsed real time was measured with the GNU time utility. The 
  throughput is reported in molecules per minute (k=thousand, m=million) as a 
  relatable metric.
  This throughput was calculated by taking the total elapsed
  time and dividing it by the number of molecule in the dataset (42704 for 
  ChEBI 149, and 1678393 for ChEMBL 22.1). Nine records skipped for SMILES input for
  \cdkversion{} is because the parser now validates on read and both ChEBI/
  ChEMBL contain invalid SMILES (9 each, they are different records). The SDfile skips
  were molecules in ChEBI with query bonds. The ChEBI SMILES input contains 
  2107 blank (but valid) inputs, this accounts for the majority skipped 
  in v1.4.19. Additional skipped records were due to failures somewhere else,
  ChEBI contains some exotic molecules causing a few skipped records where
  ChEMBL has none.

\begin{tabular}{lllrclrcll}
Benchmark  & Data Set & Input Format & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\
           &          &              & Skip & Time & Per Min & Skip  & Time  & Per Min \\
\hline
\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 22.51s   & 113k & 9    & 0.97s & 2.6m & 23.21 \\
                            &                            & 
    SDfile & 0              & 7.21s   & 355k & 25   & 3.75s & 686k & 1.92 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 8m39.3s  & 193k & 9    & 12.17s & 8.3m & 42.67 \\
                            &                              & 
    SDfile & 0              & 3m17.29s & 510k & 0    & 1m07.23 & 1.5m & 2.93 \\
\hline
\multirow{4}{*}{rings -mark} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 22.68   & 112k & 9    & 1.42s & 1.8m & 15.97 \\
                            &                            & 
    SDfile & 0              & 9.36   & 273k  & 0    & 4.37s & 568k & 2.14 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 8m41.57    & 193k & 9    & 30.58s & 3.3m & 17.06 \\
                            &                              & 
    SDfile & 0              & 4m9.82 & 403k & 0    & 1.20.60s & 1.2m & 3.10 \\
\hline
\multirow{4}{*}{rings -sssr} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 27.40s    & 93k & 9    & 1.48s & 1.7m & 18.51 \\
                            &                            & 
    SDfile & 0              & 11.85s    & 216k & 25   & 4.08s & 628k & 2.9 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 12m4.62s & 138k & 9    & 28.07s & 3.6m & 25.81 \\
                            &                              & 
    SDfile & 0              & 7m09.58s  & 234k & 0    & 1m24.16s & 1.2m & 5.10 \\
\hline
\multirow{4}{*}{rings -all} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2126           & 45.28s  & 56k & 26    & 1.27s & 2m & 35.65 \\
                            &                            & 
    SDfile & 16             & 36.56  & 70k & 40   & 4.13s & 620k & 8.85 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 88             & 12m40.20s & 132k & 9    & 26.48s & 3.8m & 28.71 \\
                            &                              & 
    SDfile & 90             & 8m05.64s  & 207k & 0    & 1m18.99s & 1.3m & 6.15 \\
\hline
\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 36.58s  & 70k & 9    & 1.83s & 1.4m & 19.99 \\
                            &                            & 
    SDfile & 0              & 21.15s  & 121k & 26   & 4.77s & 537k & 4.43 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 14             & 14m33.86s & 115k & 9    & 42.41s & 2.4m & 20.61 \\
                            &                              & 
    SDfile & 0              & 8m59.82s & 186k & 0    & 1m44.86s & 960k & 5.15 \\
\hline
\multirow{4}{*}{convert -ofmt=smi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 35.63s  & 71k & 9    & 1.37s & 1.9m & 26.01 \\
                            &                            & 
    SDfile & 35             & 20.91s  & 122k & 29   & 4.21s & 608k & 4.97 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 14             & 14m26.02s & 116k & 9    & 28.65s & 3.5m & 30.23 \\
                            &                              & 
    SDfile & 0              & 8m59.38s & 186k & 0    & 1m27.35s & 1.2m & 6.17 \\
\hline
\multirow{4}{*}{convert -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 32.42s  & 79k & 9    & 10.33s & 248k & 3.14 \\
                            &                            & 
    SDfile & 13             & 17.00s  & 150k & 29   & 14.49s & 176k & 1.17 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 14m25.82s & 116k & 9    & 5m30.66s & 304k & 2.62 \\
                            &                              & 
    SDfile & 1              & 8m51.33s & 189k & 0    & 6m50.92s & 245k & 1.29 \\
\hline
\multirow{4}{*}{convert -gen2d -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 24m28.02s  & 1.7k & 9    & 35.7s & 72k & 41.12 \\
                            &                            & 
    SDfile & 13             & 35m12.03s  & 1.2k & 29   & 42.08s & 61k & 50.19 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 3h27m07s  & 8.1k & 9    & 18m02.59s & 93k & 11.48 \\
                            &                              & 
    SDfile & 1              & 5h58m30s  & 4.6k & 0    & 19m54.12s & 84k & 18.01 \\
\hline
\multirow{4}{*}{fpgen -type=maccs} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2150           & 1h37m35s  & 438 & 9    & 19.8s & 129k & 295.71 \\
                            &                            & 
    SDfile & 48             & 1h44m17s & 409 & 25   & 22.33s & 114k & 280.21 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 214            & 20h24m57s & 1.4k  & 9    & 13m27.11s & 124k & 91.06 \\
                            &                              & 
    SDfile & 225            & 24h41m46s & 1.1k & 0    & 13m41.83s & 122k & 108.18 \\
\hline
\multirow{4}{*}{fpgen -type=path} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 1m14.50s   & 34k & 26    & 8.22s & 312k & 9.06 \\
                            &                            & 
    SDfile & 0              & 1m52.17s   & 23k & 40    & 11.67s & 220k & 9.61 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 35m02.80s       & 48k & 9    & 5m35.25s & 300k & 6.27 \\
                            &                              & 
    SDfile & 0              & 38m51.73s       & 43k & 0    & 6m7.04s & 274k & 6.35 \\
\hline
\multirow{4}{*}{fpgen -type=ecfp4} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & -              &  N/A        && 9    & 4.47s & 573k & \\
                            &                            & 
    SDfile & -              &  N/A        && 25   & 7.04s & 364k & \\
                            & \multirow{2}{*}{ChEMBL 22.1} &
    SMILES & -              &  N/A        && 9    & 2m45.68s & 608k & \\
                            &                              & 
    SDfile & -              &  N/A        && 0    & 3m59.23s & 421k & \\
\hline
\end{tabular}
